---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

set.seed(42)
```

# stdidx

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/stdidx)](https://CRAN.R-project.org/package=stdidx)
<!-- badges: end -->

This small package provides a set of simple tools for standardizing variables (based on summary statistics from another variable or a subset, such as a control group in an experiment) and constructing indices of multiple variables. It provides simple mean indexing and inverse covariance-weighted indices.

## Installation

<!-- You can install the released version of stdidx from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("stdidx") -->
<!-- ``` -->

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("graemeblair/stdidx")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(stdidx)

var1 <- rnorm(100, mean = 0.5, sd = 0.25)
var2 <- rnorm(100, mean = -1, sd = 0.5)
var3 <- rnorm(100, mean = 1, sd = 1)

idx <- idx_mean(var1, var2, var3)
head(idx)
```

`stdidx` is set up to work with a `tidyverse` workflow out of the box:

```{r tidy}
library(dplyr)

df <- tibble(var1, var2, var3)

df %>% mutate(idx_var = idx_mean(var1, var2, var3)) %>% head
```

